---
title: "miR532_BMT_peripheralblood_wk5"
author: "Patrick Lac"
date: "April 12, 2020"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

``` {r library, message = F}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
```

Let's begin by importing our data:

``` {r import.data}
metadata <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR532_BMT/Peripheral_Bleeds/Data/BMT_MetaData.csv")
JL_data <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR532_BMT/Peripheral_Bleeds/Data/JL_532_BMT_Data.csv")
MB_data <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR532_BMT/Peripheral_Bleeds/Data/MB_532_BMT_Data.csv")
PL_data <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR532_BMT/Peripheral_Bleeds/Data/PL_532_BMT_Data.csv")
```

Next lets attach the different peripheral blood data together:
``` {r combine.data}
Total_PB_data <- rbind(JL_data, MB_data, PL_data)
head(Total_PB_data)
```

We will make a copy of the total data for manipulation:
``` {r data.copy}
Data.copy <- Total_PB_data
```
What are the dimensions of our data?
```{r dim.data}
dim(Data.copy)
```

## Peripheral bleeds 5 weeks post-transplant:
Next we will filter for CBC data at 5 weeks post-transplant
``` {r filter.5weeks}
Week5 <- subset(Data.copy, Weeks.post.transplant == 5)
```

Let's check the dimensions of our subsetted data:
```{r dim.week5}
dim(Week5)
```

Let's make dotplots for our CBC counts:

``` {r wk5.WBC, fig.width=3,fig.height=3.5}
wk5.WBC <- ggplot(Week5, aes(x=Treatment, y=WBC, fill=Treatment)) +
  #Add standard deviation bars
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = 0.1, geom="errorbar", color="black", size=1.2, width=0.1) +
  #Add mean bar
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  #Add dot-plot
  geom_dotplot(binaxis="y", binwidth = 0.1, stackdir="center", stackratio=2, dotsize=3) + 
  #Set y-axis scale
  ylim(0, 12) +
  #Change Graph and axis titles
  labs(title = "White blood cells", x = "Treatment", y = "WBC (10"^"3"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  #Changing legend titles
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  #perform t-test
  stat_compare_means(method="t.test", hjust=0, vjust=0.2, size=4) +
  theme(legend.position="top", legend.title=element_text(size=15), legend.text = element_text(size=15)) +
  theme(legend.position="none")
wk5.WBC
```



```{r wk5.RBC, fig.width=3,fig.height=3}
wk5.RBC <- ggplot(Week5, aes(x=Treatment, y=RBC, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = 0.1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 0.1, stackdir="center", stackratio=2, dotsize=3.5) + 
  ylim(0, 15) +
  labs(title = "Red blood cells", x = "Treatment", y = "RBC (10"^"6"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  stat_compare_means(method="t.test", hjust=0.03, vjust=0.2, size=4) +
  theme(legend.position="none")
wk5.RBC
```



```{r wk5.HGB, fig.width=3,fig.height=3}
wk5.HGB <- ggplot(Week5, aes(x=Treatment, y=HGB, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = 0.1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 0.1, stackdir="center", stackratio=3.5, dotsize=5) + 
  ylim(0, 20) +
  labs(title = "Hemoglobin", x = "Treatment", y = "HGB (g/dL)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  stat_compare_means(method="t.test", hjust=-0.07, vjust=0.2, size=4) +
  theme(legend.position="top", legend.title=element_text(size=15), legend.text = element_text(size=15)) +
  theme(legend.position="none")
wk5.HGB
```



```{r wk5.HCT, fig.width=3,fig.height=3}
wk5.HCT <- ggplot(Week5, aes(x=Treatment, y=HCT, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = 1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 1, stackdir="center", stackratio=1.8, dotsize=2) + 
  ylim(0, 80) +
  labs(title = "Hematocrit", x = "Treatment", y = "HCT (%)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  stat_compare_means(method="t.test", hjust=0, vjust=0.2, size=4) +
  theme(legend.position="top", legend.title=element_text(size=15), legend.text = element_text(size=15)) +
  theme(legend.position="none")
wk5.HCT
```



```{r wk5.PLT, fig.width=3,fig.height=3}
wk5.PLT <- ggplot(Week5, aes(x=Treatment, y=PLT, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = 3, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 1, stackdir="center", stackratio=5, dotsize=30) + 
  ylim(0, 1250) +
  labs(title = "Platelets", x = "Treatment", y = "PLT (10"^"3"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  stat_compare_means(method="t.test", hjust=0, vjust=0.2, size=4) +
  theme(legend.position="none")
wk5.PLT
```



```{r wk5.MCV, fig.width=3,fig.height=3}
wk5.MCV <- ggplot(Week5, aes(x=Treatment, y=MCV, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = 1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 1, stackdir="center", stackratio=1.1, dotsize=0.5) + 
  ylim(35, 55) +
  labs(title = "Mean corpuscular volume", x = "Treatment", y = "MCV ("~mu~"m"^"3"*")") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  stat_compare_means(method="t.test", hjust=0, vjust=0.2, size=4) +
  theme(legend.position="none")
wk5.MCV
```



```{r wk5.MCH, fig.width=3,fig.height=3}
wk5.MCH <- ggplot(Week5, aes(x=Treatment, y=MCH, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = 0.1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 0.1, stackdir="center", stackratio=2.5, dotsize=5) + 
  ylim(0, 20) +
  labs(title = "Mean corpuscular hemoglobin", x = "Treatment", y = "MCH (pg)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  stat_compare_means(method="t.test", hjust=-0.05, vjust=0.2, size=4) +
  theme(legend.position="none")
wk5.MCH
```



```{r wk5.MCHC, fig.width=3,fig.height=3.2}
wk5.MCHC <- ggplot(Week5, aes(x=Treatment, y=MCHC, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = 0.1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 0.1, stackdir="center", stackratio=3, dotsize=10) + 
  ylim(0, 40) +
  labs(title = "Mean corpuscular \n hemoglobin concentration", x = "Treatment", y = "MCHC (g/dl)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  stat_compare_means(method="t.test", hjust=-0.05, vjust=0.2, size=4) +
  theme(legend.position="none")
wk5.MCHC
```



```{r wk5.RDW, fig.width=3,fig.height=3}
wk5.RDW <- ggplot(Week5, aes(x=Treatment, y=RDW, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = 0.1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 0.1, stackdir="center", stackratio=2.5, dotsize=6) + 
  ylim(0, 25) +
  labs(title = "RBC distribution width", x = "Treatment", y = "RDW (%)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  stat_compare_means(method="t.test", hjust=-0.05, vjust=0.2, size=4) +
  theme(legend.position="none")
wk5.RDW
```



```{r wk5.MPV, fig.width=3,fig.height=3}
wk5.MPV <- ggplot(Week5, aes(x=Treatment, y=MPV, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = 0.1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 0.1, stackdir="center", stackratio=2, dotsize=2.5) + 
  ylim(0, 10) +
  labs(title = "Mean platelet volume", x = "Treatment", y = "MPV ("~mu~"m"^"3"*")") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  stat_compare_means(method="t.test", hjust=0, vjust=0.2, size=4) +
  theme(legend.position="none")
wk5.MPV
```



```{r wk5.Percent.Lym, fig.width=3,fig.height=3.5}
wk5.Percent.Lym <- ggplot(Week5, aes(x=Treatment, y=Percent.Lym, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = 1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 1, stackdir="center", stackratio=2, dotsize=2) + 
  ylim(0, 80) +
  labs(title = "Lymphocyte frequency", x = "Treatment", y = "Lym (%)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=9)", "miR-532 (n=12)")) +
  stat_compare_means(method="t.test", hjust=-0.05, vjust=0.2, size=4) +
  theme(legend.position="bottom")
wk5.Percent.Lym
```



```{r wk5.Percent.Mon, fig.width=3,fig.height=3.5}
wk5.Percent.Mon <- ggplot(Week5, aes(x=Treatment, y=Percent.Mon, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = .1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = .1, stackdir="center", stackratio=2, dotsize=5) + 
  ylim(0, 20) +
  labs(title = "Monocyte frequency", x = "Treatment", y = "Mon (%)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=9)", "miR-532 (n=12)")) +
  stat_compare_means(method="t.test", hjust=-0.04, vjust=0.2, size=4) +
  theme(legend.position="bottom")
wk5.Percent.Mon
```



```{r wk5.Percent.Gra, fig.width=3,fig.height=3.5}
wk5.Percent.Gra <- ggplot(Week5, aes(x=Treatment, y=Percent.Gra, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = .1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 0.1, stackdir="center", stackratio=2, dotsize=20) + 
  ylim(0, 80) +
  labs(title = "Granulocyte frequency", x = "Treatment", y = "Gra (%)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=9)", "miR-532 (n=12)")) +
  stat_compare_means(method="t.test", hjust=-0.04, vjust=0.2, size=4) +
  theme(legend.position="bottom")
wk5.Percent.Gra
```



```{r wk5.Number.Lym, fig.width=3,fig.height=3}
wk5.Number.Lym <- ggplot(Week5, aes(x=Treatment, y=Number.Lym, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = .1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 0.05, stackdir="center", stackratio=3, dotsize=4) + 
  ylim(0, 8) +
  labs(title = "Lymphocyte count", x = "Treatment", y = "Lym (10"^"3"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  stat_compare_means(method="t.test", hjust=-0.04, vjust=0.2, size=4) +
  theme(legend.position="none")
wk5.Number.Lym
```



```{r wk5.Number.Mon, fig.width=3,fig.height=3}
wk5.Number.Mon <- ggplot(Week5, aes(x=Treatment, y=Number.Mon, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = .1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 0.05, stackdir="center", stackratio=1.2, dotsize=0.7) + 
  ylim(0, 1.5) +
  labs(title = "Monocyte count", x = "Treatment", y = "Mon (10"^"3"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  stat_compare_means(method="t.test", hjust=-0.02, vjust=0.2, size=4) +
  theme(legend.position="none")
wk5.Number.Mon
```



```{r wk5.Number.Gra, fig.width=3,fig.height=3}
wk5.Number.Gra <- ggplot(Week5, aes(x=Treatment, y=Number.Gra, fill=Treatment)) +
  stat_summary(fun.data=mean_sdl, fun.args=list(mult=1), binwidth = .1, geom="errorbar", color="black", size=1.2, width=0.1) +
  stat_summary(fun.y=mean, geom="crossbar", color="black", size=0.6, width=0.2) +
  geom_dotplot(binaxis="y", binwidth = 0.1, stackdir="center", stackratio=2, dotsize=2) + 
  ylim(0, 8) +
  labs(title = "Granulocyte count", x = "Treatment", y = "Gra (10"^"3"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=11)) +
  scale_fill_discrete(name="Treatment", labels = c("control (n=20)", "miR-532 (n=28)")) +
  stat_compare_means(method="t.test", hjust=-0.02, vjust=0.2, size=4) +
  theme(legend.position="none")
wk5.Number.Gra
```

### Now let's arrange the plots:
#### Figure 1
```{r figure1, fig.width=10, fig.height=11}
wk5.fig1 <- ggarrange(wk5.WBC, wk5.RBC, wk5.PLT, wk5.Number.Lym, wk5.Number.Mon, wk5.Number.Gra,
          labels = "auto",
          ncol=3, nrow=2, common.legend = T, legend="bottom")
wk5.fig1
```     

#### Figure 2
```{r figure2, fig.width=10, fig.height=11}
wk5.fig2 <- ggarrange(wk5.HCT, wk5.MPV, wk5.HGB, wk5.RDW, wk5.MCV, wk5.MCH, wk5.MCHC,
         labels = "auto",
          ncol=3, nrow=3, common.legend = T, legend="bottom")
wk5.fig2
```    

  
          

